Geographically aware estimates of remotely sensed water properties for Chesapeake Bay

### 2022-09-13 manuscript/supplement.tex
pipeline-ify ms and supp
add validation plot to supplement
cleanup best_params table

\begin{figure}[h!]
    \begin{center}
          \includegraphics[width=0.75\textwidth,keepaspectratio]{../figures/counts_obs_table}
    \end{center}    
\end{figure}

>>>>

\begin{figure}[h!]
    \begin{center}
          \includegraphics[width=0.85\textwidth,keepaspectratio]{figures/counts_obs_table}
    \end{center}    
\end{figure}

\begin{figure}[h!]
    \begin{center}
          \includegraphics[width=0.7\textwidth,keepaspectratio]{figures/_validation}
          \caption{RF predicted salinity versus test set (observed) salinity. Hatching indicates the area containing 80\% of the data points.}
    \end{center}    
\end{figure}

\begin{figure}[h!]
    \begin{center}
          \includegraphics[width=1\textwidth,keepaspectratio]{figures/rf_stats_table_0_}
    \end{center}    
\end{figure}
